*** BASIC & FUNDAMENTAL GIT COMMANDS ***
Repository Setup
git init → Initialize a new Git repository in the current folder.
git clone <url> → Clone (download) an existing repository from a remote (like GitHub).
Staging & Committing
git status → Check status of files (staged, unstaged, untracked).
git add <file> → Stage specific file(s) for commit.
git add . → Stage all changes.
git commit -m "message" → Commit staged changes with a message.
Remote Setup
git remote add origin <url> → Add a remote repository (commonly called origin).
git remote -v → View remotes linked to your local repo.
Pushing & Pulling
git push -u origin main → Push commits to remote main branch (first time with -u to set upstream).
git push → Push commits to the tracked branch on remote.
git pull → Fetch and merge changes from remote into your local branch.
git fetch → Download changes from remote without merging.
Viewing History
git log → View commit history.
git log --oneline → Condensed commit history.
*** GIT BRANCHING AND MERGING WORKFLOW ***
Branch Management
git branch branchname → creates a new branch
git checkout branchname → checks out the branch
git checkout -b newbranch → creates and checks out branch
git branch -r  → list all branches tracked by the origin.
git branch -D branchname → deletes local branch
git branch -D origin/branchname -r  → deletes remote branch tracking
git push origin -D branchname → deletes remote branch
Collaboration & Synchronization
git pull → collects the changes for the repository
Branch Comparison & Integration
git diff branchname →  diffs branchname if branched checked out is not branchname
git merge branchname →  merges branchname into checked out branch (edited)